Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-25 outputs/paper/paper.qmd
Update paper.qmd

pollu_temp %>% filter((pollutant != "CO" & pollutant != "SO2")) %>% ggplot(aes(max_temp, mean_pollution)) + geom_point(color = "#6DD6CD", alpha = 0.4) + facet_grid(. ~ pollutant) + xlab("Maximum Temperature") +  ylab("Mean Pollution") + theme_bw()
```

@@

pollu_temp %>% filter((pollutant == "CO")) %>% ggplot(aes(max_temp, mean_pollution)) + geom_point(color = "#6DD6CD", alpha = 0.4) + facet_grid(. ~ pollutant) + xlab("Maximum Temperature") +  ylab("Mean Pollution") + theme_bw()
```

@@

pollu_temp %>% filter((pollutant == "SO2")) %>% ggplot(aes(max_temp, mean_pollution)) + geom_point(color = "#6DD6CD", alpha = 0.4) + facet_grid(. ~ pollutant) + xlab("Maximum Temperature") +  ylab("Mean Pollution") + theme_bw()

>>>>

pollu_temp %>% filter((pollutant != "CO" & pollutant != "SO2") & (year > 2012 & year <= 2020)) %>% ggplot(aes(max_temp, mean_pollution)) + geom_point(color = "#6DD6CD", alpha = 0.4) + facet_grid(. ~ pollutant) + xlab("Maximum Temperature") +  ylab("Mean Pollution") + theme_bw()
```

@@

pollu_temp %>% filter((pollutant == "CO")  & (year > 2012 & year <= 2020)) %>% ggplot(aes(max_temp, mean_pollution)) + geom_point(color = "#6DD6CD", alpha = 0.4) + facet_grid(. ~ pollutant) + xlab("Maximum Temperature") +  ylab("Mean Pollution") + theme_bw()
```

@@

pollu_temp %>% filter((pollutant == "SO2")  & (year > 2012 & year <= 2020)) %>% ggplot(aes(max_temp, mean_pollution)) + geom_point(color = "#6DD6CD", alpha = 0.4) + facet_grid(. ~ pollutant) + xlab("Maximum Temperature") +  ylab("Mean Pollution") + theme_bw()
